Title Goes Here

### 2020-04-10 analysis/paper/paper.Rmd
delete some intermediate data files

```{r}
# CTRL + OPTION + i to insert a code block
library(here)
# column names should be:
# session, FirstName, AbstractTitle
SAA16 <- readxl::read_excel(here("analysis/data/SAA2016.xlsx"))
SAA17 <- readxl::read_excel(here("analysis/data/SAA2017.xlsx"))
SAA18 <- readxl::read_excel(here("analysis/data/SAA2018-finalprogram.xlsx"))
SAA19 <- readxl::read_excel(here("analysis/data/SAA2019.xlsx"))

EAA18 <- readxl::read_excel(here("analysis/data/2018 EAA.xlsx"))
CAA18 <- readxl::read_excel(here("analysis/data/2018 CAA.xlsx"))

SAA16_row <- nrow(SAA16)
SAA17_row <- nrow(SAA17)
SAA18_row <- nrow(SAA18)
SAA19_row <- nrow(SAA19)
EAA18_row <- nrow(EAA18)
CAA18_row <- nrow(CAA18)

@@

We collected lists of the people that presented research at recent SAA (2016 with `r SAA16_row` presenters, 2017 with `r SAA17_row` presenters, 2018 with `r SAA18_row` presenters, 2019 with `r SAA19_row` presenters) EAA (2018 with `r EAA18_row` presenters) and CAA (2018 with `r CAA18_row` presenters) conferences. We obtained publicly available programs of these conferences and also tidied the data into a rectangular form with variables including the primary author’s first name, last name and the title of their presentation. We used R and the gender package (Mullen 2018; Mihaljević 2019; Belvis et al. 2015) to predict the gender of all first-named presenters in our sample. We used the gender package to identify a first name as male or female, based on a probability scale computed from government records of name-gender data, specifically US Social Security Administration (SSA) baby name data [citation]. This method has the advantage of speed and ease of automation, but also some substantial limitations. We are only able to infer gender into binary male/female genders and assign probabilities for the first names into these categories. This has the unfortunate result of excluding other genders from the results, and we encourage conference organizers to collect gender data directly from participants to improve the representation of minority genders in future studies. The package often fails to classify non-English names, as the SSA data the package uses are mostly in English names. This means that people with non-English names are underrepresented in our results. To remove names where gender is ambiguous, which we define as a similar proportion of males and females having that name in the SSA data, we excluded names where the difference in proportions was less than 0.47, a figure we obtained by exploratory data analysis. It is important to note that the gender designations here are not self-identified by the presenters, but are computed probabilistically. Better quality data will come if presenters self-identify their gender, but we have no alternative because currently these data are not available. Our hope is that this work, despite its many limitations, will stimulate the collection of more reliable, justifiable, and useful data by conference organisers.

>>>>

```{r}
# CTRL + OPTION + i to insert a code block
library(here)
# column names should be:
# session, FirstName, AbstractTitle

SAA18 <- readxl::read_excel(here("analysis/data/2018 SAA Title.xlsx"))
EAA18 <- readxl::read_excel(here("analysis/data/2018 EAA.xlsx"))
CAA18 <- readxl::read_excel(here("analysis/data/2018 CAA.xlsx"))

SAA18_row <- nrow(SAA18)
EAA18_row <- nrow(EAA18)
CAA18_row <- nrow(CAA18)

@@

We collected lists of the people that presented research at recent SAA (2018 with `r SAA18_row` presenters, EAA (2018 with `r EAA18_row` presenters) and CAA (2018 with `r CAA18_row` presenters) conferences. We obtained publicly available programs of these conferences and also tidied the data into a rectangular form with variables including the primary author’s first name, last name and the title of their presentation. We used R and the gender package (Mullen 2018; Mihaljević 2019; Belvis et al. 2015) to predict the gender of all first-named presenters in our sample. We used the gender package to identify a first name as male or female, based on a probability scale computed from government records of name-gender data, specifically US Social Security Administration (SSA) baby name data [citation]. This method has the advantage of speed and ease of automation, but also some substantial limitations. We are only able to infer gender into binary male/female genders and assign probabilities for the first names into these categories. This has the unfortunate result of excluding other genders from the results, and we encourage conference organizers to collect gender data directly from participants to improve the representation of minority genders in future studies. The package often fails to classify non-English names, as the SSA data the package uses are mostly in English names. This means that people with non-English names are underrepresented in our results. To remove names where gender is ambiguous, which we define as a similar proportion of males and females having that name in the SSA data, we excluded names where the difference in proportions was less than 0.47, a figure we obtained by exploratory data analysis. It is important to note that the gender designations here are not self-identified by the presenters, but are computed probabilistically. Better quality data will come if presenters self-identify their gender, but we have no alternative because currently these data are not available. Our hope is that this work, despite its many limitations, will stimulate the collection of more reliable, justifiable, and useful data by conference organisers.
